A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-24 doc/paper.tex
Case study stuff!!!!!!!!

	\subsection{Walkthrough of the Tool} Before discussing the minutiae of tool's
	development, though, we will give a basic example of how to use the tool. For
	this, we will answer this question: \textit{ What kinds of functions do people
		use to define the condition in an IF function?} Thefull  visualization that
	answers this is available in figure \ref{fig:fullpic}; however, to understand
	the interaction, we will start from the beginning. \par

@@

	\subsection{Education} Learning by example has long been a cornerstone of
	effective teacher techniques: by showing the student a concrete example of
	something, rather than dwelling in the realm of abstract description,
	comprehension increases [I'm sure there's a cite out there somewhere.] This is
	no different in software, where every explanation of a tricky programming
	concept is much untangled by the illustrative stub. Even APIs, researchers have
	found, by the inclusion of an in-practice example of the function described.
	Spreadsheet programming, then, should not be essentially different: examples of
	spreadsheet functions in use

>>>>

	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing the minutiae of tool's
	development, though, we will give a basic example of how to use the tool. For
	this, we will answer this question: \textit{ What kinds of functions do people
		use to define the condition in an IF function?} Thefull  visualization that
	answers this is available in figure \ref{fig:fullpic}; however, to understand
	the interaction, we will start from the beginning. \par

@@

	\subsection{Education} When Robillard and Deline researched common obstacles
	for programmers learning new APIs, they concluded that one of the most important
	elements of a good API was the use of code examples to demonstrate function use.
	These examples, furthermore, come in a variety of forms: small snippets
	or tutorials that show only the intended function, sample applications that
	incorporate the function in a broader context, or even production code that
	employs the function but was not initially intended to be an illustrative 
	example \cite{robillard2011field}. Of these categories, \toolname aligns
	entirely with the last; when a user chooses to explore a particular function
	node, they will see examples of that formula as it was used in a working 
	environment, with the specifics depending on the dataset the tool is using. \par

	Furthermore, Robillard and Deline's study makes the case for examples that show
	"API usage patterns involving more than one method call" \cite{robillard2011field}.
	Examples that show only a single function, they find, are too simple, whereas those
	demonstrating the interaction of functions will equip users for more complex tasks. 
	\toolname is especially suited for this focus on combination; consider again
	the question in the walkthrough (Section \ref{sec:walkthrough}), asking
	which functions and operations are used as conditions in IF. The design of this
	tool emphasizes the connection, then, between what functions like ISNA and AND
	return and what IF accepts, and specific examples for any of these combinations
	are only a click away.
